\documentclass[sigplan,10pt]{acmart}
\pagestyle{plain}

\title{400 GB/E}
\author{Markuze Alex}
\date{September 2018}

\newcommand{\oursys}{netalloc }

\begin{document}

\maketitle
\section{Introduction}
We evaluate , the effects of a dedicated memory allocator on the Linux network stack at 100Gb/s and beyond.
We propose several optimizations which we evaluate rigorously in the next sections. We add a sclable cache for 64KB chunks of memory. The goal of this cache is to shortcut the cumbersome buddy allocator, gaining faster allocation on a single core and minimize contention on multicore. The cache is a generic magazine allocator.
The second optimization we use is adding a page\_frag based, byte grained memory allocator. The page\_frag allocator optimizes cache access patterns.
We also theorize that by using huge pages we can optimize the use of TLB and thus farther optimize the cycles/byte value.
Throughout this work, we refer to the modified kernel with the set of optimizations as \oursys.

Possible contributions listed in table \ref{tab:contributions}.
Additional open issues with small impacts listed in table \ref{tab:open_issues}.
\begin{table}[b]
\centering
\begin{tabular}{l|l}
contribution & impact \\\hline
1. locking issues in UDP TX & trivial\\
2. dedicated allocator & carefull wording needed\\
3. memory wall @400Gb/s & some solution needed\\
4. magical cache & no such thing...\\
5. UDP drops & not clear what that is.\\
\hline
\end{tabular}
\caption{\label{tab:contributions}Contribution}
\end{table}

\newpage

\input{evaluation.tex}
\input{udp_loss.tex}
\input{memory.tex}
\settopmatter{printfolios=true}
\renewcommand\footnotetextcopyrightpermission[1]{}
\end{document}
